a and generators

### 2022-05-03 documentos/generators.tex
<<<<<<<<<<<<<<< HEAD

PCE generators (hereafter PCEGs) may be characterized by its local
action on every qubit 
in the system. This action can be encoded using a multi-index $\vec\alpha$, 
as in \eqref{eq:pauli_strings}, hence each of the different $4^N$ 
multi-indices may be uniquely related to each of the PCE generators
and thus denoted as $\mcG_{\vec\alpha}$, see figures \ref{fig:A_and_PCEGs_connection} and \ref{fig:appex:twoQ_PCEGs}.
% \cpnote{
The proof is simplified if one uses the Kraus representation developed in 
\sref{sec:kraus}, so we postpone the demonstration to appendix \ref{sec:2_qubits}.
For single qubits, the identity corresponds to $\mcG_0$, shown in 
\fref{fig:one:qubit:examples}(b), whereas $\mcG_3$ is shown in in 
\fref{fig:one:qubit:examples}(c).
% }
The 2-qubits PCE generator represented in subfigure (c)
of \Fref{fig:examplesPCE} acts on the first qubit (first column) as mapping its
Bloch sphere to de $x$-axis, and on the second qubit (first row) acts an identity,
hence it is labeled $\mcG_{(1,0)}$.
See \Fref{fig:appex:twoQ_PCEGs} for the notation of all 2-qubit PCE generators.

@@

\cpnote{Revisar este párrfo. Solo ha pasado una persona por ahi}
% 
% 
% The symmetry for a PCE generator $\pceg$ is encoded in the 
% $N$-dimensional array of all $\taus$. The Cartesian grid associated with it 
% is either symmetric or anti-symmetric under reflection of the 
% indices in the $k$-th position in $\vec\alpha$. 
% Consider the map
% \begin{equation}
% % \Sigma: 
% 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
% \label{eq:Sigma}
% \end{equation}
% Indeed, any generator is a subspace containing half the elements of the full vector space.  
% Map \eref{eq:Sigma} applied to the $k$-th qubit has the following properties
% \begin{enumerate}
% \item $\Sigma(\vec\alpha)\oplus \Sigma(\vec\beta)=\vec\alpha\oplus \vec\beta$.
% \item $\Sigma(\vec\alpha)\neq\vec\alpha$
% \end{enumerate}
% From the first property, we now obtain
% \begin{equation}
% \vec\alpha=\Sigma(\vec\alpha) \oplus \Sigma(\vec0)
% \end{equation}
% We now see that, depending on whether $\Sigma(\vec0)$ belongs (respectively does not belong) to the generator,
% $\vec\alpha$ belongs to the generator if and only if $\Sigma(\vec\alpha)$ belongs (respectively does not belong) to the generator.  
%

@@

\begin{figure} % {{{
\centering
\includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
\caption{Connection between rows and columns of $a$ and single qubit PCE generators.
The rows or columns of $a$ and the diagrams of the generators are either 
symmetric or anti-symmetric under reflection.
\cpnote{Mejorar figura, poner matriz de tamano normal, poner loslabels de los generadores, mejorrar el caption, cambiar los cuadrios.}
}
\label{fig:A_and_PCEGs_connection}
\end{figure} % }}}

% \ddnote{Tengo entendido que esto se queria probar usando las simetrias, esto ya
% esta probado en la secc V}
It is worth pointing out that $\san$ (and thus $a$) [see \eref{eq:san}] 
encodes all the information of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
From the tensor power of matrix $a$ one can infer the components $\{\taus\}$ of a PCE
generator $\pceg$ by taking row (or column) $\alpha$ of $A$ and replacing
$-1$ with $0$. 
The proof is given in \appref{sec:2_qubits} and in \fref{fig:A_and_PCEGs_connection} we illustrate
this connection for the single qubit case.

% \cpnote{Sienot que no tiene flujo. Quizá se le pueda dar flujo usando el final 
% del primer parrafo}

>>>>

PCE generators (hereafter PCEGs) may be characterized by its local
action on every qubit 
in the system. This action can be encoded using a multi-index $\vec\alpha$, 
as in \eqref{eq:pauli_strings}, hence each of the different $4^N$ 
multi-indices may be uniquely related to each of the PCE generators
and thus denoted as $\mcG_{\vec\alpha}$, see figures \ref{fig:A_and_PCEGs_connection} and \ref{fig:appex:twoQ_PCEGs}.
The proof is simplified if one uses the Kraus representation developed in 
\sref{sec:kraus}, so we postpone the demonstration to appendix \ref{sec:2_qubits}.
For single qubits, the identity corresponds to $\mcG_0$, shown in 
\fref{fig:one:qubit:examples}(b), whereas $\mcG_3$ is shown in in 
\fref{fig:one:qubit:examples}(c).
The 2-qubits PCE generator represented in subfigure (c)
of \Fref{fig:examplesPCE} acts on the first qubit (first column) as mapping its
Bloch sphere to de $x$-axis, and on the second qubit (first row) acts an identity,
hence it is labeled $\mcG_{(1,0)}$.
See \Fref{fig:appex:twoQ_PCEGs} for the notation of all 2-qubit PCE generators.

@@

% \cpnote{Revisar este párrfo. Solo ha pasado una persona por ahi}
% 
% 
% The symmetry for a PCE generator $\pceg$ is encoded in the 
% $N$-dimensional array of all $\taus$. The Cartesian grid associated with it 
% is either symmetric or anti-symmetric under reflection of the 
% indices in the $k$-th position in $\vec\alpha$. 
% Consider the map
% \begin{equation}
% % \Sigma: 
% 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
% \label{eq:Sigma}
% \end{equation}
% Indeed, any generator is a subspace containing half the elements of the full vector space.  
% Map \eref{eq:Sigma} applied to the $k$-th qubit has the following properties
% \begin{enumerate}
% \item $\Sigma(\vec\alpha)\oplus \Sigma(\vec\beta)=\vec\alpha\oplus \vec\beta$.
% \item $\Sigma(\vec\alpha)\neq\vec\alpha$
% \end{enumerate}
% From the first property, we now obtain
% \begin{equation}
% \vec\alpha=\Sigma(\vec\alpha) \oplus \Sigma(\vec0)
% \end{equation}
% We now see that, depending on whether $\Sigma(\vec0)$ belongs (respectively does not belong) to the generator,
% $\vec\alpha$ belongs to the generator if and only if $\Sigma(\vec\alpha)$ belongs (respectively does not belong) to the generator.  
%

@@

\begin{figure} % {{{
\centering
\begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
\pgfmathsetmacro{\unitstep}{1.5}
% % Coordenadas   {{{
% \node at (-0.6,0.5) {(a)} ;
% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
% \begin{scope}[shift={(0,-1)}]
% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
% \end{scope}
% \begin{scope}[shift={(0,-2)}]
% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
% \end{scope}
% \begin{scope}[shift={(0,-3)}]
% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
% \end{scope} 
% \draw (0,-3) rectangle (1,1); 
% % }}}
\begin{scope}[shift={(1*\unitstep,0)}] % Identity {{{
% \begin{scope}[shift={(\unitstep*2,0)}]
\node at (-0.6,0.5) {(b)} ;
\fill[black] (0,0) rectangle (1,1);
\draw[black!10] (0,0) rectangle (1,1);
\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\draw (0,-3) rectangle (1,1); 
\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(2*\unitstep,0)}] % Dephasing {{{
\node at (-0.6,0.5) {(c)} ;
\fill[black] (0,0) rectangle (1,1);
% \draw (0,0) rectangle (1,1);
\draw[black!10] (0,0) rectangle (1,1);
\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\draw (0,-3) rectangle (1,1); 
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(3*\unitstep,0)}] % Depolarization {{{
\node at (-0.6,0.5) {(d)} ;
\fill[black] (0,0) rectangle (1,1);
% \draw (0,0) rectangle (1,1);
\draw[black!10] (0,0) rectangle (1,1);
\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\draw (0,-3) rectangle (1,1); 
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(4*\unitstep,0)}] % (e) canal malo {{{
\node at (-0.6,0.5) {(e)} ;
\fill[black] (0,0) rectangle (1,1);
% \draw (0,0) rectangle (1,1);
\draw[black!10] (0,0) rectangle (1,1);
\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\draw (0,-3) rectangle (1,1); 
\end{scope} % }}}
\end{tikzpicture} % }}}
\includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
\caption{Connection between rows and columns of $a$ and single qubit PCE generators.
The rows or columns of $a$ and the diagrams of the generators are either 
symmetric or anti-symmetric under reflection.
\cpnote{Mejorar figura, poner matriz de tamano normal, poner loslabels de los generadores, mejorrar el caption, cambiar los cuadrios.}
}
\label{fig:A_and_PCEGs_connection}
\end{figure} % }}}

% \ddnote{Tengo entendido que esto se queria probar usando las simetrias, esto ya
% esta probado en la secc V}
It is worth pointing out that $\san$ (and thus $a$) [see \eref{eq:san}] 
encodes all the information of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
From the tensor power of matrix $a$ one can infer the components $\{\taus\}$ of a PCE
generator $\pceg$ by taking row (or column) $\valpha$ of $A$ and replacing
$-1$ with $0$. 
The proof is given in \appref{sec:2_qubits} and in \fref{fig:A_and_PCEGs_connection} we illustrate
this connection for the single qubit case.
